---
title: '**Raport Data Info**'
output:
  html_document:
    df_print: paged
    theme: cosmo
    toc: true
    toc_float: true
date: '`r Sys.time()`'
params:
  df: NULL
  variables: NULL
---

This report provides a comprehensive analysis of the dataset, presented in the following sections:

- **Dimensions and Types:** Displays the size of the dataset (number of rows and columns) and the types of data it contains.
- **Missing Values:** Identifies any missing values within the dataset, summarized in a table and graph.
- **Redundant Columns:** Searches for any columns that may be redundant due to duplicate or highly similar information.
- **Outliers:** Locates values that are significantly different from the majority of values in the dataset, potentially indicating data variability or measurement errors.
- **Atypical Values:** Highlights values that don't align with the expected data patterns, suggesting possible data entry errors or other inconsistencies.

# Dim & types 

```{r, echo=FALSE}
dataset_info_list <- dataset_info(df, info = FALSE)
```
The dataset contains **`r dataset_info_list$nrow`** rows and **`r dataset_info_list$ncol`** columns.


```{r, echo=FALSE}
dataset_info_df <- data.frame(
  Feature = names(dataset_info_list$types),
  Type = dataset_info_list$types
)
rownames(dataset_info_df) <- NULL
dataset_info_df
```

# Missing values

### Table
```{r, echo=FALSE}
missing_values  <- find_missing_values(df, variables)
missing_values$Table
```

### Barplot of missing values

```{r, echo=FALSE}
message <- NULL
if(any(missing_values$Table[2] != 0)){
  missing_values$Diagram
} else{
  message <- "There are no missing values, so a barplot is not needed."
}
```
`r message`

# Redundant columns

```{r, echo=FALSE, message = FALSE, warning=FALSE, error=FALSE}
redundant_columns <- redundant_cols(df, variables)

if (identical(redundant_cols(df), character(0))){
  message <- "No reduncant columns found"
} else{
  redundant_df <- data.frame(Redundant_Columns = redundant_columns)
  redundant_df
}
```
`r message`

# Outliers

```{r, echo=FALSE, message=FALSE}
outliers_message <- outliers(df, variables)

sentences <- strsplit(outliers_message, "\\. ")[[1]]

# Extracting the column names and outlier indices from each sentence
columns <- sub("For column (.*?) potential outliers indexes:.*", "\\1", sentences)
indices <- strsplit(sub(".*indexes: (.*)", "\\1", sentences), ", ")
columns[length(columns)] <- "Based on all columns"

# Checking if the last sentence is the "no outliers found" message
if(grepl("Based on all columns: no outliers were found", sentences[length(sentences)])){
  # Handling the last sentence separately
  indices[[length(indices)]] <- "No outliers found"
}


outliers_df <- data.frame(
  Column = columns,
  Indices = sapply(indices, paste, collapse = ", ")
)

outliers_df
```
# Atypical values

Here we look at three types of analyses: integer, boolean, and numeric.

- **Integer**: This suggests that the data in the column could potentially be transformed into an integer type.
- **Boolean**: The column contains 'true'/'false' or 'yes'/'no' variations that could be converted into boolean type. '1' signifies 'true'/'false' variations, while '2' represents 'yes'/'no' variations.
- **Numeric**: The column could potentially be converted into a numeric type, often when numeric values are stored as text with a comma as the decimal separator.


```{r, echo=FALSE}
atypical_values_results <- atypical_values(df, variables)
atypical_values_df <- data.frame(atypical_values_results)
atypical_values_df <- data.frame(Variable = rownames(atypical_values_df), atypical_values_df, row.names = NULL)

atypical_values_df
```
