---
title: "**toRpEDA statistical report**"
output:
  html_document:
    df_print: paged
    theme: cosmo
    toc: true
    toc_float: true
date: '`r Sys.time()`'
params:
  df: NULL
  variables: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This report provides descriptive statistics about the dataset, presented in the following sections:

- **Descriptive statistics:** Generates descriptive statistics for a given data frame.
- **Correlation matrix:** Computes correlation matrix for numeric variables from data.
- **Histogram:** Creates a series of histogram plots for the numeric variables of a data frame.
- **Barplots:** Displays bar plots of quality columns of a dataframe.

## Descriptive statistics
### Categorical variables
```{r descriptive_stat1, results='asis', echo=FALSE}
descriptive_stats <- get_descriptive_stat(df)
for (i in 1:(length(descriptive_stats) - 1)) {
  list_name <- names(descriptive_stats)[i]
  list_values <- descriptive_stats[[i]]
  
  cat("Variable name: **", list_name, "**\n", sep="")
  print(knitr::kable(list_values, 
                      align = "c"))
}
```

### Continuous variables
```{r descriptive_stat2, results='asis', echo=FALSE}
knitr::kable(descriptive_stats[[length(descriptive_stats)]])
```

## Correlation matrix

```{r correlation_matrix, echo=FALSE, warning=FALSE}
correlation_matrix <- cor_matrix(df)
knitr::kable(correlation_matrix, 
              align = "c")
```

## Histograms

```{r histogram, echo=FALSE, warning=FALSE}
histograms <- plot_hist_vars(df)
```

## Barplots

```{r barplots, echo=FALSE, results='asis', warning=FALSE}
categorical_df <- df %>% select_if(function(col) is.factor(col) | is.character(col))
categorical_df_names = colnames(categorical_df)
for (i in 1:(length(categorical_df_names))) {
  cat("Variable name: **", categorical_df_names[[i]], "**\n", sep="")
  cat("\n")
  p <- plot_bar_qual(df, categorical_df_names[[i]])
  print(p)
}
```


